---
title: "`ggswissmaps` Intro"
author: "gibo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## Installation

You can install the package with `devtools::install_github`.

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("gibonet/ggswissmaps")
```

## Content

First of all, load the package:
```{r}
library(ggswissmaps)
```

We can use the `ls` function to look at the content:
```{r}
ls("package:ggswissmaps")
```

Or launch the help:
```{r eval = FALSE}
utils::help(package = "ggswissmaps")
```


There is some data:
```{r}
data(package = "ggswissmaps")
```




## Examples

### Using the data

```{r}
data("shp_df")
class(shp_df)
length(shp_df)
names(shp_df)

# Data description
?shp_df
```

### Some maps

```{r}
data("maps2")
names(maps2)

# By name
maps2[["g1k15"]]

# By index
maps2[[147]]
```

The objects contained in `maps2` are `ggplot` objects. They have been created with `ggplot2::ggplot` plus a `ggplot2::geom_path` layer with the data in `shp_df`. As an example, the previous map is the same as:

```{r}
ggplot(shp_df[["g1k15"]], aes(x = long, y = lat, group = group)) +
  geom_path() +
  coord_equal() +
  theme_white_f()
```


