---
title: "`ggswissmaps` data with `sf`"
author: "gibo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ggswissmaps with sf}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dev = "png"
)
```


From version `0.1.2`, `ggswissmaps` includes boundaries of Switzerland, at various levels, also in `sf` format. The 8 objects are stored in the list `shp_sf`:

```{r}
library(ggswissmaps)
# str(shp_sf)  # Very long output...

class(shp_sf)
length(shp_sf)
lapply(shp_sf, class)
names(shp_sf)
```


# Use `ggswissmaps` with `sf`

The boundaries stored in the list `shp_sf` can be used with `ggplot2::geom_sf()`:  

```{r}
library(ggplot2)
ggplot(shp_sf[["g1k15"]]) + geom_sf()
```


The green background can be removed for example with `ggswissmaps::theme_white_f()` or other `ggplot2` themes, while the green background inside the boundaries can be removed by setting `fill = NA` in `ggplot2::geom_sf()`:

```{r}
ggplot(shp_sf[["g1k15"]]) + 
  geom_sf(fill = NA) + 
  ggswissmaps::theme_white_f()
```




# Coordinate reference system (crs)

Note that all the 'sf' data frames stored in the list `shp_sf` have the coordinate reference system (crs) corrensponding to "EPSG: 21781". This can be verified with `sf::st_crs()`:

```{r}
library(sf)
st_crs(shp_sf[[1]])
```

I think that this is the "old" swiss crs, while the newest one is "EPSG: 2056". In order to change the crs we can use `st::st_transform()`:

```{r}
tmp <- st_transform(shp_sf[[1]], crs = 2056)
st_crs(tmp)
```

